The controlled choice design and private paternalism in pawnshop borrowing

### 2023-12-02 ECTA submission/donde_ecta.tex
prepare for ecta submission

 \documentclass[oneside,11pt]{article}

\input{preamble.tex}
%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{
    \externaldocument{#1}
    \addFileDependency{#1.tex}
    \addFileDependency{#1.aux}
}

%\myexternaldocument{OA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT
\begin{document}

\title{The controlled choice design and private paternalism in pawnshop borrowing\thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback. Research assistance was financed through faculty grants at ITAM. Our research partner had no say in the results.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}

%\vspace{.5in}

\maketitle
\thispagestyle{empty}
\begin{abstract}

%Many firms provide commitment devices that restrict individuals' choice, but shroud this. Shrouding suggests low demand for commitment. We show that private paternalism is beneficial in the pawnbroker context we study.

We use a novel three-armed RCT, including both forced and voluntary treatment arms, to provide a unique window into choice, heterogeneous treatment effects and paternalism in the context of pawnbroker lending. Forcing borrowers into commitment contracts with a regular repayment structure decreases the financial cost of pawn loans by 22\% inclusive of fees, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 19\%. Leveraging the special features of our experimental design, we go on to point-identify the effects of commitment on both the treated and the untreated simultaneously, along with the average selection on gains. We find large and significant effects of commitment even for borrowers who would not voluntarily choose it, and no evidence of selection on gains: borrowers who would freely choose commitment do not appear to benefit more than borrowers who would not. A detailed analysis of treatment effect heterogeneity suggests that the potential gains from targeting commitment based on observable characteristics are extremely small and that most borrowers stand to gain from a policy of universal forced commitment. %The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.

%In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.4\%, increases the likelihood of recovering their pawn by 26\%, and increases the likelihood of repeat business by almost 100\%. Using machine learning methods for estimating heterogeneous treatment effects, we find that more than {70}\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it. Those that \textit{don't} choose it are predicted to be the ones who would benefit more. Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.

%and one of the most understudied. In our context more than on half of borrowers default and lose their pawn and whatever they have paid towards recovering it. Compared to the status quo pay-at-anytime 3-month contracts, forcing borrowers to pay monthly and charge a penalty if they didn't --i.e. a commitment contract-- increased recovery of pawn by about 30\% and financial costs by 10\%. However when offered a choice between the two contracts only 10\% took the monthly payment one. A pecuniary commitment seems necessary. In an alternative arm, we made them promise to pay but removed the pecuniary penalty. This increased take up to 31\%, but had zero effect on financing cost or default. The forcing contract may be better than choice for naive present biased consumers.

\end{abstract}

\vspace{.3in}

\textbf{Keywords: } Private paternalism, choice, treatment on the untreated, heterogeneous treatment effects, commitment, overconfidence.

\textbf{JEL codes:} G41, C93, O16, G21

\pagenumbering{arabic}
\etocdepthtag.toc{mtchapter}
\etocsettagdepth{mtchapter}{subsection}
\etocsettagdepth{mtappendix}{none}

%NO MORAL HAZARD IN THE CONTRACT SINCE FULLY COLLATERALIZED
%DOUBLE FAILURE: DEMAND LOW, AND DOES NOT WORK BY PEOPLE WHO TAKE IT.
%PENALIZES THEM EVEN MORE ON SOMETHING THEY WERE ALREADY PENALIZED 
%PROPENSITY TO CHOSE.
%PULLING PUNISHMENT FORWARD --CHARGING RIGHT WHEN I MESS UP.
%MAYBE ONLY IMPATIENT AND NAIVE END IN PAWNSHOPS
%1) SELECT A RANDOM SAMPLE OF NEIGHBORHOODS, EXTERNAL VALIDITY, THE ONES THEY GO ARE NAIF AND
%HYPERBOLIC
%2) ASK TO CHOSE AMONG ALL CONTRACTS
%3) CLASSIFY SOPHISTICATION AT BASELINE
%4) HOW TO GET AT SHOCKS.  --BUT DOES NOT SQUARE WITH WHY CHARGING THEM FEES WORKE.
%do shocks vary across strata, predict shocks.
%DEEP BEHAVIORAL PAPER -- CAN WE REALLY PREDICT?

@@

\paragraph{Appraising and lending.} Lender P takes gold jewelry as collateral in exchange for a fraction of the value of the piece, in cash. No other collateral and no credit history checks are needed. The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e. a teller, see Figure \ref{PawnshopPicture}). The appraiser weighs the gold piece and runs tests on its purity. Based on these she assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece in cash to the client. The borrower signs a 2-page contract with the conditions of the loan and leaves with the cash.

\paragraph{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract. It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days' grace period. The client could make payments at the branch at any time with no penalty for pre-payment. Under this status quo contract, there are no payment reminders or any other kind of interim contact between the lender and the borrower. If the client returns to pay the principal plus the accumulated interest within 105 days, she recovers her pawn, otherwise the pawnbroker keeps the piece \textit{and} any payments already made. Before the contract expires, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and the same piece as the original contract (38\% of borrowers renew at least once with a given pawn). This contract is standard in the industry.  Pawnshops make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non-defaulted loans, and by keeping the payments made on defaulted loans.

\paragraph{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.  This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 89\% said they are pawning because of an emergency, and only 12\% stated it was to use in a ``non-urgent expense''.  When asked why they are pawning this piece, 5\% responded ``lost a family member'', ``a medical emergency'' (11\%), or ``an urgent expense'' (72\%).

\paragraph{Many borrowers lose their pawn.} Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning. One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.  %Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. 
%Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

We define a borrower's financial cost as the total monetary outflow --in cash or pawn value-- from the borrower to the lender. This includes all payments the borrower made toward interest and fees, but also the net difference between the appraised value of the pawn and the loan amount (Value-Loan) in the event of default. When there is no default the borrower gets her pawn back and there is no loss of value for the borrower. Payments towards capital are considered a cost only when the borrower defaults, as she does not get reimbursed for these. Note however that when she does not default payments to capital are not an actual outflow, as they sum up to the value of the loan the lender disbursed in the first place. The formula for financial cost for person $i$ is thus as follows: %\footnote{We alternatively defined financial cost as $\text{Financial Cost}_i = \sum_t P^I_{it} + \sum_t P^F_{it} + \sum_t P^C_{it} + \mathds{1}(\text{Default}_i) \times (\text{Value}_i)-\text{Loan}_i$, and obtained similar results.}:

\begin{align*}
    \text{Financial Cost}_i =&  \sum_t P^I_{it} +\sum_t P^F_{it}  
     + \mathds{1}(\text{Default}_i) \times (\text{Value}_i-\text{Loan}_i + \sum_t P^c_{it})
\end{align*}

@@

As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Loan term takes into account the entire loan period, including extensions of the loan through refinancing.} The standard definition is given in the following formula:

\begin{align*}
    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
\end{align*}

\vspace{.1in}

@@

\vspace{.2in}
\noindent \textbf{Treatment Arms.} Treatments were randomized at the branch-day level. Each day a computer randomly assigned which types of contracts were on offer that day in the branch, and the IT system would only offer these.  We have 3 different experimental arms\footnote{The experiment included other independent arms that involved no fee penalties and did not emphasize the structure of payments. These are being analyzed in a separate paper.}

@@

%The existence of a choice arm allows us not only to measure if there is demand for such a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects. One may worry for instance that low sophistication from pawn-loans users could lead to the `wrong' people choosing the structured commitment contract. To examine this issue, we included an arm that assigns all individuals to the commitment contract so that we are able in essence to form three counterfactual outcomes; no commitment, commitment, and the chosen commitment. This design allows us to investigate the repercussions of choice not only for those who \textit{do} choose (as is the case in a standard LATE design), but also the implications of choice for those who \textit{do not} choose. This design is innovative and critical for our purposes, as it enables us to explore whether or not forcing people into a structured payment contract could be more beneficial than allowing choice for a significant fraction of them.

@@

\paragraph{Timeline.} Figure \ref{exp_description} shows the experimental timeline along with the length of time for which we observe payments. For loans made in the first week of the experiment, we observe up to 338 subsequent days of loan information; for loans made in the last week we observe up to 235 days. Figure \ref{exp_description} also illustrates the number branch-days per arm, the number of loans, and the number of surveys. %Not every contract has a survey for several reasons, we have survey information for \hl{XXX\%} of them. There were two reasons: \hl{XXX}.

\paragraph{Explanation.} Since we are interested in measuring the effect of different contract terms on client behavior, it is important that clients understand these terms. To ensure this, we built two ``check-points'' as follows.  Two enumerators were present in each branch for the whole day during the duration of our experiment. At the first checking, these enumerators explained the contract terms to clients, emphasizing that the frequent payment contract involved the commitment to pay a third of the outstanding amount \underline{each month}, along with the nature of the fees associated with the Commitment arm. Figure \ref{ExplanatoryMaterial} presents an excerpt of the materials we used to explain the contracts, translated into English. The explanation took about 3-5 minutes and continued until the client said she understood the contract terms. Enumerators then asked clients to explain the contract back to them before correcting any misunderstandings. At the second check-point the appraiser made clients read the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip} before they signed the contract. This summary was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract. The appraiser read it aloud and then asked the client to sign it as proof of understating. %The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3). 
%Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms. The clients had to put their name on a slip of paper where they stated they promised to pay monthly.
We are confident the overwhelming majority of clients understood the contracts and that those in the choice arm made informed choices.
%\footnote{That we can systematically predict demand based on consumer characteristics and measured beliefs suggest that take up is not random.}

@@

\paragraph{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey that we implemented. The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece. These transactions include the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the item's value), the date of the pawn transaction, and the type of contract for that pawn: commitment or status quo. Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed. After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.  We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013. This includes all the pawns that took place during our experiment along with those that one month before and eight months after our experiment. Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm. The experiment comprises 8,519 pawns while our administrative data covers a total of 26,180 pawns.

\paragraph{Survey data.} An additional team of enumerators stationed in each branch asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before they learned which contracts would be available on that day. The survey was intentionally short to avoid discouraging the potential clients from pawning. It measured demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time-consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 7,210 clients, and our survey response rate was 78\% among clients who took loans.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
We only use the survey in Section \ref{Paternalism} of the paper.

@@

\paragraph{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results. The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter the branch.  If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on individual borrowers.  Narrative reports and the way the treatment was implemented make us believe that selection into treatment is unlikely.\footnote{Potential clients did not know that different days could have different contracts. If they asked, appraisers said that whatever was offered on that day was the only available contract for an undetermined length of time. Anecdotally, appraisers told us that they did not think refusals differed across arms, and our enumerators informed us that potential clients rarely left the branch without pawning. Lender P also never complained to us that our different treatments were hurting sales.}

If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms. That is, if potential borrowers disliked being forced into a commitment contract, we would expect a lower number of pawns on branch days where only the commitment contract is available compared to control days. Table \ref{attrition_table} shows that this is not the case. There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day. Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability. The differences across arms are smaller when we look at medians, or when we look at the number of borrowers pawning (some borrowers pawn more than one piece). Figure \ref{boxplot_attrition} shows that full distribution of loans per day is very similar across treatment arms. The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns identical across arms.}

@@

%As we increase the threshold on the size of the mistake necessary to be classified as having made the wrong choice, by definition the share of mistakes in both groups falls.

%Among choosers, only 18\% would have had superior outcomes had they not complied, whereas among non-choosers almost 80\% made a mistake according to this definition.  Because this arm is comprised of 89\% non-choosers, the overall rate of mistake in the arm was around 68\%.

%benefit is the case that forcing commitment generates large benefits on average, but it is also generating benefits for almost 90\% of the forced population.

>>>>

% use option [draft] for initial submission
%            [final] for the prepublication
\documentclass[ecta,nameyear,final]{econsocart}
%
%\usepackage{}
\RequirePackage[colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue,pagebackref]{hyperref}

\startlocaldefs

\usepackage{booktabs}
\usepackage{multirow}
\usepackage{float}         
\usepackage{amsmath}
\usepackage{amscd}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{dsfont}
\usepackage{colortbl}
\usepackage{comment}
\usepackage{lscape}
\usepackage{subcaption}
\newtheorem{theorem}{Theorem}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{prop}[theorem]{Proposition} 
\newtheorem{cor}[theorem]{Corollary} 
\newtheorem{assumption}{Assumption} 
\newtheorem{lem}{Lemma}

\newcommand{\wh}{\widehat}

\newcommand{\E}{\mathbb{E}}

\endlocaldefs

\usepackage[section]{placeins}

\begin{document}

\begin{frontmatter}

\title{The controlled choice design and private paternalism in pawnshop borrowing}
\runtitle{The controlled choice design and private paternalism}

\begin{aug}
% use \particle for den|der|de|van|von (only lc!)
% [id=?,addressref=?,corref]{\fnms{}~\snm{}\ead[label=e?]{}\thanksref{}}
%
%% e-mail is mandatory for each author
%
%%% initials in fnms (if any) with spaces
%
\author[id=au1,addressref={add1}]{\fnms{Craig}~\snm{McIntosh}\ead[label=e1]{ctmcintosh@ucsd.edu}}
\author[id=au2,addressref={add2}]{\fnms{Isaac}~\snm{Meza}\ead[label=e2]{isaacmezalopez@g.harvard.edu}}
\author[id=au3,addressref={add3}]{\fnms{Joyce}~\snm{Sadka}\ead[label=e3]{jsadka@itam.mx}}
\author[id=au4,addressref={add4}]{\fnms{Enrique}~\snm{Seira}\ead[label=e4]{enrique.seira@gmail.com}}
\author[id=au5,addressref={add5}]{\fnms{Francis J.}~\snm{DiTraglia}\ead[label=e5]{francis.ditraglia@economics.ox.ac.uk}}

% Addresses
\address[id=add1]{%
\orgdiv{Department of Economics}
\orgname{University of California San Diego}}

\address[id=add2]{%
\orgdiv{Department of Economics}
\orgname{Harvard University}}

\address[id=add3]{%
\orgdiv{Department of Economics}
\orgname{Instituto Tecnologico Autonomo de Mexico}}

\address[id=add4]{%
\orgdiv{Department of Economics}
\orgname{Michigan State University}}

\address[id=add5]{%
\orgdiv{Department of Economics}
\orgname{University of Oxford}}
\end{aug}

%% Put support info here. Reminder: do not thank the handling coeditor anonymously or by name
\support{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback. Research assistance was financed through faculty grants at ITAM. Our research partner had no say in the results.}
%
\coeditor{\fnm{[Name} \snm{Surname}; will be inserted later]}

\begin{abstract}
We use a novel three-armed RCT, including both forced and voluntary treatment arms, to provide a unique window into choice, heterogeneous treatment effects and paternalism in the context of pawnbroker lending. Forcing borrowers into commitment contracts with a regular repayment structure decreases the financial cost of pawn loans by 22\% inclusive of fees, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 19\%. Leveraging the special features of our experimental design, we go on to point-identify the effects of commitment on both the treated and the untreated simultaneously, along with the average selection on gains. We find large and significant effects of commitment even for borrowers who would not voluntarily choose it, and no evidence of selection on gains: borrowers who would freely choose commitment do not appear to benefit more than borrowers who would not. A detailed analysis of treatment effect heterogeneity suggests that the potential gains from targeting commitment based on observable characteristics are extremely small and that most borrowers stand to gain from a policy of universal forced commitment.
\end{abstract}

\begin{keyword}
\kwd{Private paternalism}
\kwd{choice}
\kwd{treatment on the untreated}
\kwd{heterogeneous treatment effects}
\kwd{commitment}
\kwd{overconfidence}
\end{keyword}

\end{frontmatter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Main text entry area:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\noindent \textbf{Appraising and lending.} Lender P takes gold jewelry as collateral in exchange for a fraction of the value of the piece, in cash. No other collateral and no credit history checks are needed. The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e. a teller, see Figure \ref{PawnshopPicture}). The appraiser weighs the gold piece and runs tests on its purity. Based on these she assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece in cash to the client. The borrower signs a 2-page contract with the conditions of the loan and leaves with the cash.

\noindent \textbf{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract. It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days' grace period. The client could make payments at the branch at any time with no penalty for pre-payment. Under this status quo contract, there are no payment reminders or any other kind of interim contact between the lender and the borrower. If the client returns to pay the principal plus the accumulated interest within 105 days, she recovers her pawn, otherwise the pawnbroker keeps the piece \textit{and} any payments already made. Before the contract expires, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and the same piece as the original contract (38\% of borrowers renew at least once with a given pawn). This contract is standard in the industry.  Pawnshops make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non-defaulted loans, and by keeping the payments made on defaulted loans.

\noindent \textbf{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.  This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 89\% said they are pawning because of an emergency, and only 12\% stated it was to use in a ``non-urgent expense''.  When asked why they are pawning this piece, 5\% responded ``lost a family member'', ``a medical emergency'' (11\%), or ``an urgent expense'' (72\%).

\noindent \textbf{Many borrowers lose their pawn.} Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning. One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.  %Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. 
%Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

We define a borrower's financial cost as the total monetary outflow --in cash or pawn value-- from the borrower to the lender. This includes all payments the borrower made toward interest and fees, but also the net difference between the appraised value of the pawn and the loan amount (Value-Loan) in the event of default. When there is no default the borrower gets her pawn back and there is no loss of value for the borrower. Payments towards capital are considered a cost only when the borrower defaults, as she does not get reimbursed for these. Note however that when she does not default payments to capital are not an actual outflow, as they sum up to the value of the loan the lender disbursed in the first place. The formula for financial cost for person $i$ is thus as follows: %\footnote{We alternatively defined financial cost as $\text{Financial Cost}_i = \sum_t P^I_{it} + \sum_t P^F_{it} + \sum_t P^C_{it} + \mathds{1}(\text{Default}_i) \times (\text{Value}_i)-\text{Loan}_i$, and obtained similar results.}:
\begin{align*}
    \text{Financial Cost}_i =&  \sum_t P^I_{it} +\sum_t P^F_{it}  
     + \mathds{1}(\text{Default}_i) \times (\text{Value}_i-\text{Loan}_i + \sum_t P^c_{it})
\end{align*}

@@

As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Loan term takes into account the entire loan period, including extensions of the loan through refinancing.} The standard definition is given in the following formula:
\begin{align*}
    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
\end{align*}

\begin{figure}
    \begin{center}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
        \caption{}
    \end{subfigure}
     \begin{subfigure}{0.45\textwidth}
       \centering
      \includegraphics[width=\textwidth]{Figuras/hist_apr.pdf}
      \caption{}
    \end{subfigure}
    \end{center}
 \caption{Financial cost. Panel (a) presents a histogram of financial cost for the control group. The figure plots separately the financial cost separately for borrowers who lose the pawn (blue) and those that recover it (transparent).  Panel (b) is analogous but displays the APR.}
     \label{fc_hist}
      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
\end{figure}

@@

\noindent \textbf{Treatment Arms.} Treatments were randomized at the branch-day level. Each day a computer randomly assigned which types of contracts were on offer that day in the branch, and the IT system would only offer these.  We have 3 different experimental arms\footnote{The experiment included other independent arms that involved no fee penalties and did not emphasize the structure of payments. These are being analyzed in a separate paper.}

@@

\begin{figure}     
\begin{center}
\begin{subfigure}{\textwidth}
        \includegraphics[width=\textwidth]{Figuras/consort.pdf}
    \end{subfigure}
  \end{center}
 \caption{Experiment description}
     \label{exp_description}
%\textit{Do file: }  \texttt{ss\_att.do}
\end{figure}

@@

\noindent \textbf{Timeline.} Figure \ref{exp_description} shows the experimental timeline along with the length of time for which we observe payments. For loans made in the first week of the experiment, we observe up to 338 subsequent days of loan information; for loans made in the last week we observe up to 235 days. Figure \ref{exp_description} also illustrates the number branch-days per arm, the number of loans, and the number of surveys. %Not every contract has a survey for several reasons, we have survey information for \hl{XXX\%} of them. There were two reasons: \hl{XXX}.

\noindent \textbf{Explanation.} Since we are interested in measuring the effect of different contract terms on client behavior, it is important that clients understand these terms. To ensure this, we built two ``check-points'' as follows.  Two enumerators were present in each branch for the whole day during the duration of our experiment. At the first checking, these enumerators explained the contract terms to clients, emphasizing that the frequent payment contract involved the commitment to pay a third of the outstanding amount \underline{each month}, along with the nature of the fees associated with the Commitment arm. Figure \ref{ExplanatoryMaterial} presents an excerpt of the materials we used to explain the contracts, translated into English. The explanation took about 3-5 minutes and continued until the client said she understood the contract terms. Enumerators then asked clients to explain the contract back to them before correcting any misunderstandings. At the second check-point the appraiser made clients read the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip} before they signed the contract. This summary was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract. The appraiser read it aloud and then asked the client to sign it as proof of understating. %The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3). 
%Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms. The clients had to put their name on a slip of paper where they stated they promised to pay monthly.
We are confident the overwhelming majority of clients understood the contracts and that those in the choice arm made informed choices.
%\footnote{That we can systematically predict demand based on consumer characteristics and measured beliefs suggest that take up is not random.}

@@

\noindent \textbf{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey that we implemented. The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece. These transactions include the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the item's value), the date of the pawn transaction, and the type of contract for that pawn: commitment or status quo. Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed. After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.  We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013. This includes all the pawns that took place during our experiment along with those that one month before and eight months after our experiment. Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm. The experiment comprises 8,519 pawns while our administrative data covers a total of 26,180 pawns.

\noindent \textbf{Survey data.} An additional team of enumerators stationed in each branch asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before they learned which contracts would be available on that day. The survey was intentionally short to avoid discouraging the potential clients from pawning. It measured demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time-consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 7,210 clients, and our survey response rate was 78\% among clients who took loans.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
We only use the survey in Section \ref{Paternalism} of the paper.

@@

\noindent \textbf{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results. The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter the branch.  If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on individual borrowers.  Narrative reports and the way the treatment was implemented make us believe that selection into treatment is unlikely.\footnote{Potential clients did not know that different days could have different contracts. If they asked, appraisers said that whatever was offered on that day was the only available contract for an undetermined length of time. Anecdotally, appraisers told us that they did not think refusals differed across arms, and our enumerators informed us that potential clients rarely left the branch without pawning. Lender P also never complained to us that our different treatments were hurting sales.}

If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms. That is, if potential borrowers disliked being forced into a commitment contract, we would expect a lower number of pawns on branch days where only the commitment contract is available compared to control days. Table \ref{attrition_table} shows that this is not the case. There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day. Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability. The differences across arms are smaller when we look at medians, or when we look at the number of borrowers pawning (some borrowers pawn more than one piece). Figure \ref{boxplot_attrition} shows that full distribution of loans per day is very similar across treatment arms. The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns becomes identical across arms.}

\begin{table}
\caption{Limited and balanced attrition}
\label{attrition_table}
\begin{center}
\scriptsize{\input{./Tables/Attrition.tex}}
\end{center}
\legend{Each row in this table 
 corresponds to a regression. The dependent variables are: the number of pawns-loans originated per day per branch, the number of borrowers per day-branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey. Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice). The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients. Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.}
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

@@
